\Title

### 2016-02-22 manuscript/manuscript.tex
Paragraphs about model and data in CRUST1 synthetic
Also some tweaks to the simple synthetic test, particularly including
the initial estimate used.

We test and illustrate the proposed inversion method
by applying it to two noise-corrupted synthetic data sets.
The first data set is generated by a simple Moho model simulating the transition
from a thicker continental crust to a thinner oceanic crust.
This application uses cross-validation to estimate the regularizing parameter
($\mu$) while assuming that the anomalous Moho density-contrast ($\Delta\rho$)
and the Normal Earth Moho depth ($z_{ref}$) are known quantities.
The second data set is generated by a more complex model derived from
the CRUST1.0 model \citep{laske2013}.
This application uses cross-validation to estimate all three hyper-parameters:
$\mu$, $\Delta\rho$, and $z_{ref}$.
The model is restricted to South America and is meant to simulate
with more fidelity the real data application.

@@

We separated the synthetic data into training and testing data sets
following Fig.~\ref{fig:grid_separation}.
The training data set is a regular grid of
$N_{lat} \times N_{lon} = 40 \times 50$ points
(a total of $N_{train} = 2000$).
The testing data set is composed of $N_{test} = 5821$ observations.
We used cross-validation to estimate an optimal regularization parameter ($\mu$)
from a set of $N_\mu = 16$ values equally spaced on a logarithmic scale
between $10^{-6}$ and $10^{-1}$.
We ran our regularized inversion on the training data set
for each value of $\mu$,
obtaining 16 Moho depth estimates.
We computed the mean square error (MSE, Eq.~\ref{eq:msemu}) for each estimate.
The final estimated Moho depth is the one that minimizes the MSE.

@@

>>>>

We test and illustrate the proposed inversion method
by applying it to two noise-corrupted synthetic data sets.
The first data set is generated by a simple Moho model simulating the transition
from a thicker continental crust to a thinner oceanic crust.
This application uses cross-validation to estimate the regularizing parameter
($\mu$) while assuming that the anomalous Moho density-contrast ($\Delta\rho$)
and the Normal Earth Moho depth ($z_{ref}$) are known quantities.
This first test is simplified in order to investigate solely
the efficiency of the inversion and
the cross-validation procedure to estimate $\mu$.
The second data set is generated by a more complex model derived from
the South American portion of the global CRUST1.0 model \citep{laske2013}.
This application uses cross-validation to estimate all three hyper-parameters:
$\mu$, $\Delta\rho$, and $z_{ref}$.
The model and corresponding synthetic data are meant to simulate
with more fidelity the real data application.

@@

We separated the synthetic data into training and testing data sets
following Fig.~\ref{fig:grid_separation}.
The training data set is a regular grid of
$N_{lat} \times N_{lon} = 40 \times 50$ points
(a total of $N_{train} = 2000$).
The testing data set is composed of $N_{test} = 5821$ observations.
We used cross-validation to estimate an optimal regularization parameter ($\mu$)
from a set of $N_\mu = 16$ values equally spaced on a logarithmic scale
between $10^{-6}$ and $10^{-1}$.
We ran our regularized inversion on the training data set
for each value of $\mu$,
obtaining 16 Moho depth estimates.
For all inversions, the initial Moho depth estimate
used to start the Gauss-Newton optimization
was set to 60 km depth for all inversion parameters.
Finally, we computed the mean square error (MSE, Eq.~\ref{eq:msemu})
for each estimate and chose as the final estimated Moho model
the one that minimizes the MSE.

@@

In this test, we simulate the anomalous Moho of South America
using the Moho depth of the CRUST1.0 model
\citep[][ Fig.~\ref{fig:crust1-data}a]{laske2013}.
The Normal Earth Moho is $z_{ref} = 30\ km$ and
the density-contrast is $\Delta\rho = 350\ kg/m^3$.
We forward model the gravitational attraction of the anomalous Moho
on a regular grid of $N_{lat} \times N_{lon} = 159 \times 119$ points
(a total of 18921 observations) at a constant height of 50 km.
We contaminate the synthetic data with normally distributed pseudo-random noise
with zero mean and 5 mGal standard deviation (Fig.~\ref{fig:crust1-data}b).

The cross-validation procedure to determine $\Delta\rho$ and $z_{ref}$
requires knowledge of the Moho depth at certain points,
usually from seismic experiments.
Thus, we must also generate synthetic seismic data about the Moho depth.
We produce such data by interpolating the Moho depth shown in
Fig.~\ref{fig:crust1-data}a on the same geographic coordinates as the
data from \citet{assumpcao2012}.
The resulting synthetic seismic data is shown in Fig.~\ref{fig:crust1-data}c.
